Measuring individual differences in the understanding of gaze cues

### 2023-03-20 paper/manuscript.Rmd
correct link to github

The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
The data sets generated during and/or analysed during the current study are available in the [gazecues-methods] repository (<https://github.com/jprein/gazecues-methods>).
All experiments were pre-registered (<https://osf.io/zjhsc/>).

>>>>

The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
The data sets generated during and/or analysed during the current study are available in the [gazecues-methods] repository (<https://github.com/ccp-eva/gazecues-methods>).
All experiments were pre-registered (<https://osf.io/zjhsc/>).
